Discriminant Function Analysis 
========================================================
From: http://www.statmethods.net/advstats/discriminant.html

Linear Discriminant Analysis with Jacknifed Prediction
-------------------------------------------------------
```{r}
library(MASS)
mydata <- iris

fit <- lda(Species ~ Sepal.Length + Sepal.Width + Petal.Length, data=mydata,
   na.action="na.omit", CV=TRUE)
fit
```
Assess the accuracy of the prediction percent correct for each category of G

```{r}
ct <- table(mydata$Species, fit$class)
diag(prop.table(ct, 1))
```
total percent correct
```{r}
sum(diag(prop.table(ct)))
```

** To Do: do a MANOVA for significance test. ** 

Quadratic Discriminant Function
-------------------------------

Quadratic Discriminant Analysis with 3 groups applying resubstitution prediction and equal prior probabilities.
```{r}
fit2 <- qda(Species ~ Sepal.Length + Sepal.Width + Petal.Length, data=na.omit(mydata), prior=c(1,1,1)/3)
fit2
ct2 <- table(mydata$Species, predict(fit2,mydata)$class)
diag(prop.table(ct2, 1))
#total percent correct
sum(diag(prop.table(ct2)))
```

Visualizing the Results
-----------------------
Scatter plot using the 1st two discriminant dimensions

```{r}
plot(fit2) # fit from lda ??? did not work
# Panels of histograms and overlayed density plots
# for 1st discriminant function
plot(fit2, dimen=1, type="both") # fit from lda #does not work with the plot function!!!
```

The partimat( ) function in the klaR package can display the results of a linear or quadratic classifications 2 variables at a time.

Exploratory Graph for LDA or QDA
```{r}
library(klaR)
partimat(Species ~ Sepal.Length + Sepal.Width + Petal.Length,data=mydata,method="lda")
```

You can also produce a scatterplot matrix with color coding by group.

Scatterplot for 3 Group Problem
```{r}
pairs(mydata[c("Sepal.Length", "Sepal.Width","Petal.Length")], main="Iris data", pch=22,bg=c("red", "yellow", "blue")[unclass(mydata$Species)]) 
```