party: A Laboratory for Recursive Partytioning
========================================================
This is to further understand the the ctree functionality. 
I am following the party package manual.
These are some of the examples in there.
```{r}
rm(list=ls())
library(party)
library(psych)
data("treepipit", package="coin")
str(treepipit)
describeBy(treepipit, treepipit$Count)
ct <- ctree(counts~., data=treepipit)
```

```{r fig.width=7, fig.height=6}
plot(ct)
plot(ct, terminal_panel = node_hist(ct, breaks=0:6-0.5, ymax=65,horizontal=FALSE, freq=TRUE))
```

#### Trying a Linear Model to confirm varible significance.

```{r}
lm.model <- lm(formula=counts~., data=treepipit)
summary(lm.model)
```

Glucoma and laser scanning images
==================================
```{r}
data("GlaucomaM", package="TH.data")
#describeBy(GlaucomaM,group=GlaucomaM$Class)
describe(GlaucomaM)
str(GlaucomaM)
gt <- ctree(Class ~., data=GlaucomaM, controls=ctree_control(minsplit=50))
plot(gt)
```

#### Linear Model for the same
```{r}
data.GlaucomaM <- GlaucomaM
data.GlaucomaM$Class <- as.numeric(data.GlaucomaM$Class)
#g.lm <- lm(formula=Class ~ ., data=data.GlaucomaM)
g.lm2 <- lm(formula=Class ~ vari * vasg * tms, data=data.GlaucomaM)
#summary(g.lm)
summary(g.lm2)
```
**Dropping** _tms_
```{r}
g.lm3 <- lm(formula=Class ~ vari * vasg, data=data.GlaucomaM)
#summary(g.lm)
summary(g.lm3)
```

**Looking at split statitics(verbatim from the text)**
```{r fig.height=12}
cex <- 1.6
inner <- nodes(gt, c(1,2,5))
layout(matrix(1:length(inner), nrow=length(inner)))
out <- sapply(inner, function(i) {
  splitstat <- i$psplit$splitstatistic
  x <- data.GlaucomaM[[i$psplit$variableName]][splitstat>0]
  plot(x, splitstat[splitstat >0], main = paste("Node", i$nodeID),
       xlab= i$psplit$varibleName, ylab ="Statistic", ylim=c(0,10),
       cex.axis = cex, cex.lab = cex, cex.main=cex)
  abline(v=i$psplit$splitpoint, lty = 3)
})
```

**Estimated conditional class probabilities**
```{r}
prob <- sapply(treeresponse(gt), function(x) x[1]) + runif(nrow(data.GlaucomaM), min=-0.01, max=0.01)
splitvar <- nodes(gt, 1)[[1]]$psplit$variableName
plot(data.GlaucomaM[[splitvar]], prob, pch = as.numeric(data.GlaucomaM$Class), col= as.numeric(data.GlaucomaM$Class), ylab = "Conditional Class Prob.", xlab = splitvar)
abline(v=nodes(gt, 1)[[1]]$psplit$splitpoint, lty=2)
legend(0.15, 0.7, pch=1:2, col=1:2, legend = levels(GlaucomaM$Class), bty="n")
```

**Predictions for the learning class;**
```{r}
table(Predict(gt), GlaucomaM$Class)
```

Node positive breast cancer
===========================

```{r}
data("GBSG2", package="TH.data")
str(GBSG2)
help(GBSG2)

describeBy(GBSG2, group=list(GBSG2$tgrade, GBSG2$menostat))

library(ggplot2)
sp <- ggplot(data=GBSG2, aes(x=time,y=age)) + geom_point()
sp <- sp + facet_grid(menostat ~ tgrade) + ylab("Age") + xlab("Recurrence free survival time (days)")
sp

#stree <- ctree(Surv(time, cens) ~ ., data=GBSG2)
#plot(stree)

```

